Penelitian Mandiri Sains Komputasi I

### 2023-05-22 Thesis/Penelitian Mandiri I/Penelitian Mandiri 1 Present/Week I/Update Progress.Rmd
Update dulu

---
title: "Penelitian Mandiri Sains Komputasi I"
subtitle: "Update Progress Minggu I"
author: "Mohammad Rizka Fadhli<br>Ikang"
institute: "20921004@mahasiswa.itb.ac.id"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  xaringan::moon_reader:
    mathjax: default
    lib_dir: libs
    css: [default,"footer-header.css", fc, fc-fonts]
    seal: true
    nature:
      ratio: '18:10'
      slideNumberFormat: '%current%' 
      highlightStyle: ir-black
      highlightLines: true
      countIncrementalSlides: false
---
layout: true

@@

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

>>>>

---
title: "Penelitian Mandiri Sains Komputasi I"
subtitle: "Update Progress Minggu I"
author: "Mohammad Rizka Fadhli<br>Ikang"
institute: "20921004@mahasiswa.itb.ac.id"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  xaringan::moon_reader:
    mathjax: default
    lib_dir: libs
    css: [default,"footer-header.css", fc, fc-fonts]
    seal: true
    nature:
      ratio: '18:10'
      slideNumberFormat: '%current%' 
      highlightStyle: ir-black
      highlightLines: true
      countIncrementalSlides: false
    includes:
      after_body: insert-logo.html
---
layout: true

@@

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

# reference:
# https://www.garrickadenbuie.com/blog/xaringan-tip-logo-all-slides/
```
